Influence of galaxy rotation and outflows in the Lyman-$\alpha$ spectral line

### 2017-03-02 paper/paper.tex
rewriting intro

\title{Influence of galaxy rotation and outflows in the Lyman Alpha spectral line}
\shorttitle{Influence of galaxy rotation and outflows in the Lyman Alpha spectral line}

\shortauthors{Remolina-Gutierrez et al.}

@@

Galaxies are key to understand our Universe. However, distant ones are very challenging to detect. It is then an open challenge to obtain as much information as possible from them, as they represent the younger stages of galaxy evolution. Astronomers noted that a that relevant fraction of these galaxies emitted a really strong line at $1215.67\;\AA$ in their spectra at  and named them Lyman Alpha Emitters (LAEs). The purpose of this paper is to use this spectral line to model and simulate LAEs in order to narrow computationally their physical and kinematic properties. \\

>>>>

\title{Influence of galaxy rotation and outflows in the Lyman-$\alpha$
  spectral line}
\shorttitle{Rotation and outflows in the Lyman-$\alpha$ lines}

\shortauthors{Remolina-Gutierrez and Forero-Romero.}

@@

Distant galaxies are key to understand early evolutionary stages of
our Universe.
However, those galaxies are challenging to detect.
Physical conditions in those galaxies allows the emergence of
Lyman-$\alpha$ line emission at $1216$ \AA \cite{PartrigePeebles}.
Galaxies detected through its Lyman-$\alpha$ emission receive the name of
spectra at  and named Lyman Alpha Emitters (LAEs).
